---
title: "cw10-stats614"
author: "Jared 'Jay' Klein"
date: "11/9/2021"
output: word_document
---

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
tribble(~WorkExperience, ~LevelofEducation, ~AnnualIncomeThou,
        21,                      6,               31.7,
        14,                      3,               17.9,
        4,                       8,               22.7,
        16,                      8,               63.1,
        12,                      4,               33,
        20,                      4,               41.4,
        25,                      1,               20.7,
        8,                       3,               14.6,
        24,                      12,              97.3,
        28,                       9,              72.1,
        4,                       11,              49.1,
        15,                       4,              52
)->X
X
```

1)  Use and show R code to produce a full Multiple Regression Model. The 
response variable is Annual Income.  Also produce the summary table

```{r}
lm(AnnualIncomeThou~LevelofEducation + WorkExperience, X) ->dat_modello

summary(dat_modello)
```


2)  Use and show R code to produce a full Multiple Regression Model that 
includes and interaction term. Also produce the summary table

```{r}
lm(AnnualIncomeThou~LevelofEducation + WorkExperience + LevelofEducation:WorkExperience, X) ->dat_modello_due

summary(dat_modello_due)
```



3)  Using summary indicators from both models determine which model you 
would use to predict Annual Income.  Justify your answer.  Your analysis should 
have 6 to 7 sentences using and comparing significance of pvalues, R2, adusted R2, 
variable standard errors, residual standard errors and the overall significance of 
both models.

I would choose to use the initial multiple linear regression model (titled "dat_modello")
as the model that would best predict Annual income. This is based on a number of factors.
For example, the p-value for the coefficients in this model are both significant to at least
0.05 significance level and includes a general p-value for the whole model that is closer
to zero. While the R2 and adjusted R2 values are compariable (off by minute values), the
significance attached to the independent variables put the first model over the top. Furthermore,
the high degree of freedom on the first model (2-9 compared to 3-8) generally indicates 
a larger sample size and thus more power to accept or reject the null hypothesis. 

