---
title: "hw-ch6-STAT614"
author: "Jared 'Jay' Klein and Khairiya Eidan"
date: "10/14/2021"
output: word_document
---

#########################
1)

a) Null Hypothesis - Ho : μ = 501 (null hypothesis)
     
    Alternative Hypothesis - Ha : μ < 501 (alternative hypothesis)


b) 
t = (485 - 501)/se , se = 116/sqrt(100)
se = 11.5 -> t = (485 - 501)/11.6

df = n - 1 -> df = 99

t = -1.379 df = 99

c) 
P-value = (left tail) 0.0855

d) 0.0855 > 0.05, we fail to reject the null hypothesis
##########################

2)
```{r}
library(tidyverse)
mtcars
```

a) qsec is the quarter mile time of the cars within the dataset. 

b)
```{r}
qqnorm(mtcars$qsec)
```

c)
```{r}
hist(mtcars$qsec)
```
d) The quartile plot of qsec is normal because it has its plots in a reltiavely straight diagonal line. 
The histogram is also normal as it is bell-hsaped and relatively symmetrical. 
The data is showed NOT to be skewed in either direction meaning that the mean is 
about to or equal to the median. 

e) 

Null Hypothesis - the qsec indicator for the population of vehicles is equal to 16.
Ho = 16

Alternative Hypothesis - the qsec indicator for the population of vehicles is greater than 16.
Ha > 16

```{r}
t.test(mtcars$qsec, mu = 16, alternative = "greater", conf.level = .95)
```

Since the outcome of the test outputs a P-value < .05 consistent with the confidence level, we can reject the null hypothesis (Ho).

If we ran the tests however many times on samples of the dataset we can be 95% confident that we would get the same conclusion each time (ie. that the qsec indicator for the population of vehicles is greater than 16). 

#########################
3)

a) 
```{r}
prop.test(x=75, n=150, p=.45, alternative = "greater", correct = FALSE)
```
P-value = 0.1092

b)
```{r}
prop.test(x=75, n=150, p=.45, alternative = "less", correct = FALSE)
```
p-value = 0.8908

c)
```{r}
prop.test(x=75, n=150, p=.45, alternative = "two.sided", correct = FALSE)
```
p-value = 0.2184

d) No

###########################
4) 

Null hypothesis - 65 percent of adults in the United States reported that math skills were very critical or important to their job. 
Ho = 65

Alternative Hypothesis - the number of adults in the United States that report math skills as critical or important to their job increased.
Ha > 65

```{r}
prop.test(x=297, n=480, p=.65, alternative = "greater", conf.level = .95, correct = FALSE)
```

P-value = 0.9244, the 95% confidence interval is .5817 - 1.0000, z-stat is 1.435409

We do not have enough evidence to reject the null hypothesis as the p-value result is more than 0.05
##########################
5)
#Ho : μ = 2000
#Ha : μ ≠  2000

y(bar) = 1500, n = 10, s = 100

Ho: mew = 2000

t = (1500 - 2000)/se, se = 100/sqrt(10)
    (1500 - 2000)/31.62
    
t = -15.81
(right tail) = .9999
One-tailed probability (left tail): 	0.00000004
Two-tailed probability: 	0.00000007

It is highly likely that the mean income for graduate managers  is less than or(and?) not equal to $2000 a month. 
We reject the null hypothesis, based on the p-value is appears that the mean is less than $2000. 

B) The P-value for a less than 2000 Ha is 0.0000004, this is less than 0.05 which suggests that the null hypothesis can be rejected and the alternative hypothesis accepted. 

C) The P-value for a more than 2000 Ha is 0.999999, this is more than 0.05 which suggests that the null hypothesis cannot be rejected. 

