---
title: "classwork6"
author: "Jared 'Jay' Klein"
date: "10/12/2021"
output: word_document
---

1) The “fun size” of a Snickers bar is supposed to weigh 20 grams.  Because the 
penalty for selling candy bars under their advertised weight is severe, the 
manufacturer calibrates the machine so that the mean weight is 20.1 grams.  
The quality-control engineer at M&M – Mars,  the Snickers manufacturer, is 
concerned about the calibration.  He obtains a random sample of 11 candy bars, 
weights them, and obtains the data given below:

19.6  20.66  19.56  19.98  20.65  19.61  20.55  20.36  21.02  21.50  19.74

The engineer conducts the one-sample t test at the α = 0.01 level of 
significance. The engineer is trying to determine if the machine delivers a 
weight of 20.1 or not. Assume that the standard conditions for executing a 
t test are satisfied

a) State the appropriate null hypothesis and alternative hypothesis
  
  Null Hypothesis - The established belief is that the machine  weighing 
  Snickers candy bars weigh delivers a weight of 20 grams. 
  
  Alt. Hypothesis - the hypothesis is that the machine is instead calibrated to
  deliver candy bars over 20.1 grams. Ha: mew > 20.1 
  
b)  Show and use R code to create a vector for the data set.
```{r}
candy_vector <- c(19.6,20.66,19.56,19.98,20.65,19.61,20.55,20.36,21.02,21.50,19.74)
```

c)  Show and use R code to run the one sample t test.
```{r}
t.test(candy_vector, mu=20.1, alternative="greater", conf.level = .95)
```

d)  What is the t statistic, the p value, and the 95% confidence interval
  
  t-stat: 0.99028
  df: 10
  p-value: 0.1727

e)  Should the null hypothesis be rejected?  Why or Why not?

No, the p-value is greater than .05 and we thus fail to reject the null hypothesis


2) Use and show R code to execute a significance test for proportions for each case. 
Identify the p value and determine if you should reject or fail to reject the 
null hypothesis
   a)  Ho :  π = .6   vs   Ho :  π < .6 ,    n = 250 , x = 124 ,       α = .01
```{r}
prop.test(x = 124, n = 250, p = .6, alternative="less", conf.level = .95, correct = FALSE)
```
   
   The null hypothesis can be rejected where p-value = 0.0003946 < .05.
   
   b)  Ho :  π = .45   vs   Ho :  π  > .45 ,    n = 68 , x = 30 ,      α = .05
```{r}
prop.test(x = 30, n = 68, p = .45, alternative="greater", conf.level = .95, correct = FALSE)
```
   
   The null hypothesis cannot be rejected because p-value = 0.558 > .05.
   
   c)   Ho :  π = .9   vs   Ho :  π  ≠ .p ,       n = 500 , x = 440 ,   α = .05
```{r}
prop.test(x = 440, n = 500, p = .9, alternative="two.sided", conf.level = .95, correct = FALSE)
```

The null hypothesis cannot be rejected because p-value = 0.136 > .05. 

3)  *True or False   
A Type One Error is committed when the null hypothesis is rejected when it is 
in fact true.

This is TRUE. 



