---
title: "HW1 - 614"
author: "Jared 'Jay' Klein"
date: "8/31/2021"
output: word_document
---

1)  Use and show R code to evaluate the following expression:[ln(120)]^3 -  π
```{r}
desired_value <- (abs(log(120))^3) - pi
print(desired_value)
```

2)  Use and show R code to round your answer from number 1 to the nearest hundredth.
```{r}
print(round(desired_value, digits = 2))
```
3)  Use and show R code to produce all even integers greater than 7 but less than 101.
```{r}
c <- vector()
for (variable in 8:100) {
  if (variable %% 2 == 0) {
    c <- append(c, variable)
  }
}

print(c)
```
4)  Use and show R code to find the mean of all positive integers less than 100.
```{r}
another_c <- vector()
for (i in 0:99) {
  another_c <- append(another_c, i)
}

print(mean(another_c))
```

```{r}
help("seq")
```

5) For the given data set below, Use and show R code to create a vector and assign the vector to variable,{10, 22, 24, 34, 35, 39, 41, 43, 44, 45.5, 47, 51, 53, 54.5, 55, 56.75, 58, 58.3, 59, 59}
```{r}
mommys_favorite_vector <- c(10, 22, 24, 34, 35, 39, 41, 43, 44, 45.5, 47, 51, 53, 54.5, 55, 56.75, 58, 58.3, 59, 59)
```
5a)  Use and show R code to find the median for the data set.
```{r}
median(mommys_favorite_vector)
```
5b) Use and show R code to produce a boxplot for the data set.
```{r}
boxplot(mommys_favorite_vector)
```
5c) Use and show R code to find the mean, median, maximum, minimum, 1stquartile and the 3rd quartile for the data set.
```{r}
summary(mommys_favorite_vector)
```
5d) Use and show R code to produce a histogram. 
```{r}
hist(mommys_favorite_vector)
```
Data is skewed to the left. 

6) This is a long question so I won't copy paste here. 
```{r}
my_credit_score_is_better_than_these_not_bragging <- c(545, 595, 640, 675, 705, 750)

interest_rates_i_never_understand <- c(18.982, 17.976, 12.218, 8.612, 6.680, 5.150)

plot(my_credit_score_is_better_than_these_not_bragging, interest_rates_i_never_understand)
```


