---
title: "HW1-Khairiya-Jay"
author: "Khairiya Eidan, Jared 'Jay' Klein"
date: "9/3/2021"
output: word_document
---

1)  Use and show R code to evaluate the following expression:[ln(120)]^3 -  π
```{r}
desired_value <- ((log(120))^3)-pi
print(desired_value)
```

2)  Use and show R code to round your answer from number 1 to the nearest hundredth.
```{r}
round(desired_value, digits = 2)
```
3)  Use and show R code to produce all even integers greater than 7 but less than 101.
```{r}
seq(8,100,2)
```
4)  Use and show R code to find the mean of all positive integers less than 100.
```{r}
E <- c(0:99)
mean(E)
```

5) For the given data set below, Use and show R code to create a vector and assign the vector to variable,{10, 22, 24, 34, 35, 39, 41, 43, 44, 45.5, 47, 51, 53, 54.5, 55, 56.75, 58, 58.3, 59, 59}
```{r}
q5_vector <- c(10, 22, 24, 34, 35, 39, 41, 43, 44, 45.5, 47, 51, 53, 54.5, 55, 56.75, 58, 58.3, 59, 59)
```
5a)  Use and show R code to find the median for the data set.
```{r}
median(q5_vector)
```
5b) Use and show R code to produce a boxplot for the data set.
```{r}
boxplot(q5_vector)
```
5c) Use and show R code to find the mean, median, maximum, minimum, 1stquartile and the 3rd quartile for the data set.
```{r}
summary(q5_vector)
```
5d) Use and show R code to produce a histogram. 
```{r}
hist(q5_vector)
```
Data is skewed to the left. 

6 Use and show R code to produce a scatter plot for the following bivariable data set.  
Let Credit Score be the independent values x and Interest Rate be the dependent values y.
```{r}
X <- c(545,595,640,675,705,750)
Y <- c(18.982,17.976,12.218,8.612,6.680,5.150)

plot(X,Y)
```
Does your scatter plot suggest a positive or a negative association between the variables?
It suggests a negative association.