---
title: "classwork5-STAT614"
author: "Jared 'Jay' Klein"
date: "9/28/2021"
output: word_document
---


```{r}
?prop.test
```

1a)
```{r}
sample_size = 200
sample_prop = .07*sample_size

prop.test(x=sample_prop, n=sample_size, conf.level = .95 )
```
 0.04025812 0.11705481


1b)
```{r}
sample_size = 500
sample_prop = .07*sample_size

prop.test(x=sample_prop, n=sample_size, conf.level = .95 )
```
 0.04991248 0.09693342


1c)
```{r}
sample_size = 800
sample_prop = .07*sample_size

prop.test(x=sample_prop, n=sample_size, conf.level = .95 )
```
 0.05374762 0.09050618


1d)
```{r}
sample_size = 1100
sample_prop = .07*sample_size

prop.test(x=sample_prop, n=sample_size, conf.level = .95 )

1.95/sqrt(61/640000) 
```
0.05596248 0.08712002

1e)

As we increased hte sample size  of students for the study, it appears as if the confidence intervals are becoming more and more narrow. That is, the difference between the upper bound and lower bound of the interval is coming closer and closer together. 

1f) 

As I alluded to in 1e, it appears that as the sample size of students increases each time, the width or difference between the upper bound and lower bound of the confidence interval becomes more and more narrow. It seems that as this happens (the sample size going up) we get a more accurate idea of the pi-hat we used in class (population proportion?). 

2a)
```{r}
# Compute Standard Error
se <- 4/sqrt(27)

# Get T distribution factor and set y_bar which is the given sample mean
#t <- 2.056
#t <- qt(.95, 26, lower.tail = TRUE)
alpha <- (1-.95)/2

t <- qt(p=alpha, df=26, lower.tail = FALSE)


y_bar <- 42

# Create your boundries, multiply Standard Error by distribution factor
upper_bound <- 42 + (t*se)
lower_bound <- 42 - (t*se)

library(glue)

glue("({lower_bound}, {upper_bound}), with T-dist value as {t}")
```
(40.4176527003631, 43.5823472996369), with T-dist value as 2.05552943864287


2b)
```{r}
# Compute Standard Error
se <- 4/sqrt(27)

# Get T distribution factor and set y_bar which is the given sample mean

alpha = (1-.9)/2
t <- qt(p=alpha, df=26, lower.tail = FALSE)
y_bar <- 42

# Create your boundries, multiply Standard Error by distribution factor
upper_bound <- 42 + (t*se)
lower_bound <- 42 - (t*se)

library(glue)

glue("({lower_bound}, {upper_bound}), with T-dist value as {t}")
```
(40.6870147131898, 43.3129852868102), with T-dist value as 1.70561791975927

3)

FALSE, this is not guaranteed.  
