---
title: "hw9-stats614"
author: "Jared 'Jay' Klein"
date: "10/29/2021"
output: word_document
---

```{r}
library(tidyverse)
library(dplyr)
```


1)

```{r}
tribble(~Year, ~RateofReturnSP500, ~RateofReturnofGE,
                    1996, .203, .402,
                    1997, .310, .510,
                    1998, .267, .410,
                    1999, .195, .536,
                    2000, -.101, -.060,
                    2001, -.130, -.151,
                    2002, -.234, -.377,
                    2003, .264, .308,
                    2004, .090, .207,
                    2005, .030, -.014,
                    2006, .128, .093,
                    2007, -.035, .027,
                    2008, -.385, -.593,
                    2009, .235, -.102,
                    2010, .067, .053) -> index_
```


1a)
```{r}
ggplot(data = index_) +
  geom_point(mapping = aes(x = RateofReturnSP500, y = RateofReturnofGE))
```

1b)
Based on the pattern in the above plot I believe that the possibility of a lin
-ear relationship is strong. 

1c)
```{r}
cor(index_$RateofReturnSP500, index_$RateofReturnofGE)
```

1d)
The output coefficent of .8841227 indicates that ther is likely at least a moderate
positive correlation. 

1e)

```{r}
summary(lm(formula = RateofReturnofGE~RateofReturnSP500, data=index_))
```

1f)

Regression equation -> -0.001227  + 1.402002RateOfReturnOfSP500 = RateOfReturnOfGE

1g)

For every increase in the rate of return of GE, the rate of return of the SP500 increases by 1.402002.

1h) 

```{r}
ggplot(data = index_) +
  geom_point(mapping = aes(x = RateofReturnSP500, y = RateofReturnofGE)) +
  geom_smooth(method = lm, mapping = aes(x = RateofReturnSP500, y = RateofReturnofGE), se=FALSE)

```
 
 
1i)

.-0.001227  + 1.402002RateOfReturnOfSP500 = RateOfReturnOfGE

.-0.001227  + 1.402002*1.78 = GE
-0.001227 + 2.495564 = GE
2.494337 = GE

1ii)

observed-SP500 -> .267

.-0.001227  + 1.402002RateOfReturnOfSP500 = expectedRateOfReturnOfGE

.-0.001227  + 1.402002*.410 = expectedGE

0.5735938

Observed - Expected

.267 - 0.5735938 = 0.3065938

The residual of .306 is above the average. 

1k)

```{r}
summary(lm(RateofReturnSP500 ~ RateofReturnofGE, data=index_))
```


The proportion of the variability of our dependent variable explained by the linear
regression model is .78 (multiple r-squared statistic) which indicates that model
does a fairly good job of answer the regression question.

2a)

  i) (20 GDP, 90 Cell)
  ii) (36 GDP, 42 Cell)
  
2b)

Observedy -> 45.1

Expectedy = -.13 + 2.62(34.3)
Expectedy = 89.7

45.1 - 89.7 = -44.6

The residual is -44.6 which means that the observered value is below the average
predicted by the linear model. 

2c)

The correlation is positive, given the prediction equation in the previous question.
As you increase GDP (x), Cell use increases (Y). Judging from the plot, the relationship
is moderate rather than strong. 

3a)

Question: As Gii increases, Fertility will increase as well. Is there a positive 
linear relationship between the two variables?

3b)

```{r}
gii <- c(0.42, 0.81, 0.11, 0.06, 0.07, 0.44, 0.14, 0.19, 0.26, 0.32)
fertility <- c(2.8, 2.2, 1.9, 1.4, 1.8, 1.8, 1.6, 1.9, 1.9, 1.7)

cor(gii, fertility)

summary(lm(fertility ~ gii))
```

prediction equation -> 1.6435 + 0.9095*gii = fertility

3c) 

Our multiple r-squared value is 0.3036.

3d)

The results of these tests and outputs seems to indicate there is NOT a linear relationship
between GDP and Fertility. At best, there may be a weak negative relationship, but more work
is required to even support that theory. 
