---
title: "cw9-stat614"
author: "Jared 'Jay' Klein"
date: "11/2/2021"
output:
  word_document: default
  html_document: default
---

```{r}
library(tidyverse)
library(dplyr)
```

```{r}
wut_ <- tribble(~HEIGHT,	~WEIGHT,	~HEADCIRCUMFERENCE,
30,	339,	47,
26.25,	267,	42,
25,	289,	43,
27,	332,	44.5,
27.5,	272,	44,
24.5,	214,	40.5,
27.75,	311,	44,
25,	259,	41.5,
28,	298,	46,
27.25,	288,	44,
26,	277,	44,
27.25,	292,	44.5,
27,	302,	42.5,
28.25,	336,	44.5
)
```

1)  Use and show R code to construct a coefficient matrix. Is there multicollinearity involving any of the explanatory variables?  If so, what variables are of concern? (Head Circumference is the response variable)
```{r}
cor(wut_)
```

Weight and Height appear to have high collinearity with Head Circumference.

2) Use and show R code to produce the full multi regression model where the response variable is Head Circumference and the two explanatory variables are Height and Weight.
```{r}
lm(HEADCIRCUMFERENCE ~ HEIGHT + WEIGHT, data = wut_) -> head_c_model
head_c_model
```


3) Use and show R code to produce the summary table for your full model.  Indicate the variable whose p value is not significant at the level of .05.  And also indicate what proportion of the variability in Head Circumference is explained by your model.
```{r}
summary(head_c_model)
```

It seems like like WEIGHT is not significant at a level of .05 with regards to 
head circumference. The proportion of variability in head circumfrence that is
explained by the model is 0.7826.


4) Use and show R code that will produce a linear regression model with the explanatory variable of no significance removed.
```{r}
lm(formula = HEADCIRCUMFERENCE ~ HEIGHT, data = wut_) -> head_c_model_no_weight
head_c_model_no_weight
```

A.	Interpret the slope of this model
    
    hEADCIRCUMFERENCE = 16.382 + 1.0157(height)

    For every 1 value (component/measure) of height, the circumference of the head
    increases by 1.0157. 
    
    
B.	What proportion of the variability of the response variable is not explained by the linear regression model? (SHOW ALL OF YOUR WORK)
```{r}
summary(head_c_model_no_weight)
```
The proportion of the variability of the head circumference of the child not explained
by the linear regression model is around 0.7584 or about 76%. 

C.	Find the correlation coefficient r  for the linear model.
```{r}
cor(wut_$HEADCIRCUMFERENCE, wut_$HEIGHT)
```


D.	Does r suggest a linear relationship that is weak, moderate, strong, or very strong?

    R Suggests a strong relationship between headcircumference and height

E.	What is the value of the standard error for the explanatory variable?  Explain what it means in two or sentences.

  Standard error lets us know how accurate a sample distribution reflects a population.
  In this case, the std error of the explanatory variable HEIGHT is .1655 which indicates
  high significance. 
