---
title: "cw11-stat614"
author: "Jared 'Jay' Klein"
date: "11/17/2021"
output: word_document
---

1. **Use and show R code to Create a data frame for the collection of vectors above.**
```{r}
library(tidyverse)

Gender<-c("Female","Female","Female","Female","Female","Female","Female","Female","Female","Female",
          "Male","Male","Male","Male","Male","Male","Male","Male","Male","Male")

MRICount<-c(816932,951545,991305,833868,856472,852244,790619,866662,857782,948066,949395,1001121,
            1038437,965353,955466,1079549,924059,955003,935494,949589)

IQ <- c(133,137,138,132,140,132,135,130,133,133,140,140,139,133,133,141,135,139,141,144)
```

2. **Use and show R code to produce a Multiple Linear Regression Model.**

```{r}
df <- data.frame(Gender, MRICount, IQ)

factor(df$Gender)

lm(IQ ~ MRICount + Gender, df) -> mlr_model
mlr_model

contrasts(as.factor(df$Gender))
```

3. **Use and show R code to produce summary indicators for your model. What is the pvalue for your model?  What is the Multiple Rsquared value for your model?**

```{r}
summary(mlr_model)
```

*The P-value of the model is 0.0231, the M R-squared of the model is 0.3581.*

4. **Use your regression model to predict IQ for a Female who has an MRICount of 855000**

```{r}
predict(mlr_model, data.frame(Gender="Female", MRICount=855000))
```
```{r}
1.191e+02 + 2.486e+00*0 + 1.735e-05 * 855000
```

E(IQ) = 1.191e+02 + 2.486e+00(GenderMale) + 1.735e-05(MRICount)

*The model predicts that the IQ of a Female with MRICount of 855000 is about 134.*

5.  ***Do you thinK that this is a good model.  Justify your answer.***

*No the model is not very good. Thought the p-value is < .05, none of the explanatory variables have any sort of significance at that .05 level. Furthermore, the model has an extremely poor R-Squared and Adjusted R-Squared values at around 35% and 28% respectively. It tells us that the e-variables are not very good at explaining IQ level.*
