---
title: "stat614-anova-2"
author: "Jared 'Jay' Klein and Khairiya Eidan"
date: "12/5/2021"
output: word_document
---

```{r}
library(tidyverse)
```

1)  What two factors have a possible impact on the cost of an oil change?
*Location and Service Center*
  
2) Prepare the data for R input. Initial rows and columns have been done for you. Complete the table.
```{r}
tribble(~ServiceCenter, ~Location,  ~OilChangeCharge,
        "Specialty Chain", "Chicago",     19.95,
        "Specialty Chain", "Chicago",     27.95,
        "Specialty Chain", "Chicago",     23.99,
        "Specialty Chain", "Bolingbrook", 23.99,
        "Specialty Chain", "Bolingbrook", 29.95,
        "Specialty Chain", "Bolingbrook", 28.99,
        "Specialty Chain", "Peoria",      24.99,
        "Specialty Chain", "Peoria",      26.99,
        "Specialty Chain", "Peoria",      19.95,
        "General Service", "Chicago",     21.99,
        "General Service", "Chicago",     26.95,
        "General Service", "Chicago",     24.95,
        "General Service", "Bolingbrook", 22.45,
        "General Service", "Bolingbrook", 29.95,
        "General Service", "Bolingbrook", 28.13,
        "General Service", "Peoria",      22.99,
        "General Service", "Peoria",      24.95,
        "General Service", "Peoria",      27.99
) -> oil
oil  
```

3)  Use and show R code to formally convert the character variables to factors.
```{r}
as.factor(oil$ServiceCenter) -> oil$ServiceCenter
as.factor(oil$Location) -> oil$Location
str(oil)
```

4) Use and show R code to produce a Two Way ANOVA Table
```{r}
aov(OilChangeCharge ~ ServiceCenter + Location + ServiceCenter:Location, 
    data = oil)-> yawn
yawn
summary(yawn)
```

5) Does your ANOVA table indicate that there is interaction for the explanatory factor variables?  Justify your answer.
*The anova table does nto indicate interaction for our terms given the high p-value (.854) associated with the interaction. At a significance level of 0.05 we cannot reject the null hypothesis.*

6) Use and show R code to produce an interaction plot.  Provide an interpretation of your interaction plot.
```{r}
interaction.plot(oil$ServiceCenter, oil$Location, oil$OilChangeCharge, xlab = "ServiceCenter",
                 ylab = "OilChangeCharge")
```
*The plot suggests a low interaction between location and service center since the lines are wack.*

7) Should the null hypothesis be rejected for your individual factors?  Justify your answers.
**
