---
title: "hw12-stat614"
author: "Jared 'Jay' Klein and Khairiya Eidan"
date: "12/5/2021"
output: word_document
---

```{r}
library(tidyverse)
```

```{r}
alaska <- c(5.41, 5.39, 4.90, 5.14, 4.80,5.24)
florida <- c(4.87,5.18,4.40,5.12,4.89,5.06)
texas <- c(5.46, 6.29, 5.57, 5.15,5.45,5.30)
```

1a)  State the appropriate null and alternative hypothesis for the one-way ANOVA procedure.

**ho: The mean ph for Alaska, Florida, and Texas are all the same.**

**ha: At least one mean ph for Alaska, Florida, and Texas are different from the others**

1b) Use the R code illustrated in class to produce the ANOVA table.
```{r}
combined_states <- data.frame(cbind(alaska, florida, texas))
stacked_states <- stack(combined_states)

aov(values~ind, data = stacked_states) -> Are
Are
summary(Are)
```

1c)  Which value is SST (Sum of Squares Treatment) in the produced ANOVA table?
**1.167**

1d)  What is the F statistic and the p value?
**F-state -> 5.811**
**P-value -> 0.0135**

1e)  State your decision to reject or fail to reject the null hypothesis.  Justify your answer.
**We reject the null hypothesis partly because it is highly unlikely three populations have a mean that is the same, but also because the p-value of 0.0135 is significant at a 0.05 level.**

2a) Missing in the table is the value for Mean Square Residuals.  This is also called Means Square Errors in 
some ANOVA output tables.  Find the Mean Square Residuals.
**MSE = SSE/(n-k)**
**MSE = 121.75/9**
```{r}
121.75/9
```


2b)  Find the F value (F statistic)
**F-stat = MST/MSE**
**F-stat = 27.58/13.52778**
```{r}
27.58/13.52778
```


2c)  Using the output shown in the ANOVA table, decide if the null hypothesis that all population means are 
equal should be rejected at the .05 level of significance.    Justify your answer. 
**The null hypothesis cannot be rejected given taht the p-value is not significant at a level of 0.05.**