---
title: "cw7-stats614"
author: "Jared 'Jay' Klein"
date: "10/20/2021"
output: word_document
---

```{r}
f_students <- c(.588, .652, .442, .293, .340, .636, .391, .367, .377, .481, .613, .274,
 .646, .403, .377, .380, .403, .617, .434, .443)

m_students <- c(.375, .256, .427, .654, .563, .405, .374, .465, .402, .373, .488, .337, .224, .477, .655)
```

```{r}
t.test(f_students, m_students, mu = 0, alternative = "two.sided", var.equal = TRUE, conf.level = .95)
```
```{r}
0.4578500-0.4316667 
```


Null Hypothesis -> Ho: mew_f = mew_m -> there is no significant difference between
  the reaction time of females (mew_f) and males (mew_m).
  
Alternative Hypothesis -> Ha: mew_f ≠ mew_m -> there is a significant difference between
  the reaction time of females (mew_f) and males (mew_m).
  
p-value -> 0.5389; t-stat -> 0.62095; conf-interval -> -0.05960489, 0.11197155

Since the p-value is > the significance level of .05 we fail to reject the null hypothesis. 
Also, since the difference of Ho (mew_f - mew_m) falls within the confidence interval, we have 
additional justification for not rejecting the null hypothesis. 